Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive/negative ASD diagnosis for GLAD/EDGI prepan
Added chunk to get positive ADHD diagnosis for GLAD/EDGI prepan

>>>>

```{r Get ASD positive for GLAD/EDGI}

GLAD.prepan_ASD_positive <- GLAD.prepan %>%
  select(autism_spectrum_disorder_numeric) %>% 
  filter(autism_spectrum_disorder_numeric == 1)

GLAD.prepan_ASD_positive <- GLAD.prepan_ASD_positive %>% 
  summarise("ASD" = n())

```{r Get ADHD positive for GLAD/EDGI}

GLAD.prepan_ADHD_positive <- GLAD.prepan %>%
  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)

GLAD.prepan_ADHD_positive <- GLAD.prepan_ADHD_positive %>% 
  summarise("ADHD" = n())
